Optimal (Multiway) Spatial Joins

### 2024-06-04 msj.tex
yufei

This section supplies the proofs postponed from Section~\ref{sec:hv:type2}. The order of the proofs here will not strictly follow the sequence in which they are referenced in Section~\ref{sec:hv:type2}. In particular, we will prove Lemma~\ref{lmm:hv:type2:properties} before Lemma~\ref{lmm:hv:type2:recur-output}, because the claims of the former lemma can be used to construct a simple argument for the latter.

@@

\extraspacing \underline{\em Proof of Statement (1).} Consider any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. The point $h' \cap v$ is covered by all of $r_1,...,r_{k-3}$. Let $h$ be the full segment of $h'$. As $h$ contains $h'$, we have $h \cap v = h' \cap v$.

@@

\extraspacing \underline{\em Proof of Statement (2).} Take any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in \J_2$. Set $p = h \cap v$, and define $h'$ as the trimmed segment of $h$. We first argue that the $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v)$ belongs to $\J(R_1,...,R_{k-3}, H', V)$, or equivalently, the point $h' \cap v$ falls in all of $r_1,...,r_{k-3}$. The subsequent discussion will show that $h' \cap v$ is in fact the same point as $p = h \cap v$. From $(r_1,...,r_{k-2},h,v) \in \J(R_1,...,R_{k-2},H,V)$, we already know that $p$ falls in all of $r_1,...,r_{k-2}$. It will then follow that $r_1,...,r_{k-3}$ all cover $h' \cap v$.

@@

As $h'$ is contained in $h$, for proving $h' \cap v = p$, it suffices to explain why $p$ is on $h'$. Let us represent $h$ as $[x_1,x_2] \times y$. Accordingly, the segment $h'$ can be written as $[x_1, x_2'] \times y$ for some $x_2' \in [x_1, x_2]$. By the definition of a trimmed segment, $(x_2',y)$ is the rightmost point on $h$ that falls in a left-end covering rectangle of $h$ in $R_{k-2}$. As $(r_1,...,r_{k-2},h,v) \in \J_2$, we know that $r_{k-2}$ is a left-end covering rectangle of $h$, and $r_{k-2}$ covers $p$ (which is a point on $h$). Therefore, the x-coordinate of $p$ cannot exceed $x_2'$, allowing us to assert that $p$ is on $h'$.

Next, we argue that $r_{k-2}\in \contained_{R_{k-2}}(\bm{t})$. Let $p'$ be the left endpoint of $h$. Because we already know $h' \cap v = h \cap v = p$, the effective horizontal segment of $\bm{t}$ is the segment $p'p$. To prove $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$, we need to explain why $r_{k-2}$ covers this segment. This is true because:

>>>>

We start by presenting two properties underneath the procedures designed in Section~\ref{sec:hv:type2}. These properties will enable us to construct simpler proofs later.

\begin{proposition} \label{prop:app:hv:type2:help1}
    Consider any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in \J2$. Define $h'$ as the trimmed segment of $h$. It holds that $h \cap v = h' \cap v$.
\end{proposition}

\begin{proof}
    Set $p = h \cap v$. As $h'$ is contained in $h$, for proving $p = h' \cap v$, it suffices to explain why $p$ is on $h'$. Let us represent $h$ as $[x_1,x_2] \times y$. Accordingly, the segment $h'$ can be written as $[x_1, x_2'] \times y$ for some $x_2' \in [x_1, x_2]$. By the definition of a trimmed segment, $(x_2',y)$ is the rightmost point on $h$ that falls in a left-end covering rectangle of $h$ in $R_{k-2}$. As $(r_1,...,r_{k-2},h,v) \in \J_2$, we know that $r_{k-2}$ is a left-end covering rectangle of $h$, and $r_{k-2}$ covers $p$ (which is a point on $h$). Therefore, the x-coordinate of $p$ cannot exceed $x_2'$, allowing us to assert that $p$ is on $h'$.
\end{proof}

We now proceed to elaborate the proofs postponed from Section~\ref{sec:hv:type2}. The order of the proofs here will not strictly follow the sequence in which they are referenced in Section~\ref{sec:hv:type2}. In particular, we will prove Lemma~\ref{lmm:hv:type2:properties} before Lemma~\ref{lmm:hv:type2:recur-output}, because the claims of the former lemma can be used to construct a simple argument for the latter.

@@

\extraspacing \underline{\em Proof of Statement (1).} Take any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. The point $h' \cap v$ is covered by all of $r_1,...,r_{k-3}$. Let $h$ be the full segment of $h'$. As $h$ contains $h'$, we have $h \cap v = h' \cap v$.

@@

\extraspacing \underline{\em Proof of Statement (2).} Take any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in \J_2$. Set $p = h \cap v$, and define $h'$ as the trimmed segment of $h$. We first argue that the $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v)$ belongs to $\J(R_1,...,R_{k-3}, H', V)$, or equivalently, the point $h' \cap v$ falls in all of $r_1,...,r_{k-3}$. By Proposition~\ref{prop:app:hv:type2:help1}, $h' \cap v$ is the same point as $p$. From $(r_1,...,r_{k-2},h,v) \in \J(R_1,...,R_{k-2},H,V)$, we know that $p = h \cap v$ falls in all of $r_1,...,r_{k-2}$. It thus follows that $r_1,...,r_{k-3}$ all cover $h' \cap v$.

@@

Next, we argue that $r_{k-2}\in \contained_{R_{k-2}}(\bm{t})$. Let $p'$ be the left endpoint of $h$. Because$h' \cap v = h \cap v = p$, the effective horizontal segment of $\bm{t}$ is the segment $p'p$. To prove $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$, we need to explain why $r_{k-2}$ covers this segment. This is true because:
